---
title: "Assignment B-1"
output: github_document
date: "2022-11-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Introuction 
Have you ever forgotten your dice at home but remembered to bring your laptop to a D&D session? Are you tired of simple addition and wish that someone could do just one step of combat for you? Then this function is for you! 

note that for this document to work you'll need the tidyverse and testthat packages 
```{r}
suppressWarnings(library(testthat))
suppressPackageStartupMessages(suppressWarnings(library(tidyverse)))
```

#### Use the function 
It's easy! Simply enter your attack modifier, then the enemy AC, and R will print out if it hits or misses! 
It looks something like this: 
For a +2 to hit against and enemy with an 18 AC: 
attack(2, 18)

Here's the function: 
```{r}
#' D20 attack: Hit or miss? 
#' 
#' Enter an attack modifier,  enemy AC, and see if your attack hits or misses. 
#' It "rolls" the 20 sided dice for you (by picking a random number from 1-20), 
#' adds your modifier, and sees if that result is greater than 
#' or equal to the enemy AC. 
#' 
#' @param mod (this is your attack modifier)
#' @param ac  (this is the enemy AC)
#'
#' @return Prints "hit!" or "miss!" depending on if the total "attack roll" is >= the AC of the "monster"
#' 
#' @example attack(3, 15)
#' 
#' @export
#' 
attack <- function(mod, ac) {
  if (!is.numeric(mod)) {
    stop("Your input must be numbers!")
  }
  if (!is.numeric(ac)) {
    stop("Your input must be numbers!")
  }
  if((sum(sample(1:20, 1)+mod)) >= ac) 
    print ("Hit!") 
  else 
    print ("Miss!")
}
```

#### Testing 

Does it work in general? 

```{r}
test_that("Does it print?", expect_output(attack(2, 15)))
```


```{r}
test_that("Misses work", {expect_equal(attack(0, 100), "Miss!")})
```

```{r}
test_that("Hits work", {expect_equal(attack(100, 10), "Hit!")})
```
Here's an example that show my custom error code: 

```{r error=TRUE}
attack("x", 10)
```

And here's some error tests in general: 
```{r}
test_that("throws error", expect_error(attack(10, 10, 10)))
```

```{r}
test_that("throws error", expect_error(attack(ten, ten)))
```

