---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## DiceRoller Function info 

<!-- badges: start -->
<!-- badges: end -->

Have you ever forgotten your dice at home but remembered to bring your laptop to a D&D session? Are you tired of simple addition and wish that someone could do just one step of combat for you? Then this function is for you! 

Simply enter your attack modifier, then the enemy AC, and R will print out if it hits or misses! 

#### Installation

You can install DiceRoller from github with:

``` r
install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-mollym1")
```

#### Example

Lets say you have an attack modifier of +2, and the enemy AC is 18:

```{r example}
library(DiceRoller)
attack(2,18)
```

Prints "hit!" or "miss!" depending on if the total "attack roll" (which is the sum of your d20 roll and your modifier) is >= the AC of the "monster". If your attack roll is >= monster AC, prints "Hit!" Otherwise, prints "Miss!". Ties print "Hit!", per the rules in the *Dungeon Masters Guide*. 
